Recent advances in smartphone computational photography

### 2020-09-24 paper.tex
Section Draft update

The majority of digital image sensors in digital cameras and phones use a Bayer filter mosaic pattern to arrange RGB color filters on the sensor. The pattern consists of 50\% green, 25\% red, and 25\% blue pixels \cite{wiki:BayerFilter}. This ratio emulates the color sensitivity of the human eye. Due to this pattern on the sensor, the raw output of a digital camera also has each pixel filtered to only red, green, or blue and a demosaicing algorithm must be used to interpolate the other values for each pixel \cite{wiki:BayerFilter}.

@@

Background information on demosaicing. Some of this will come from \cite{wiki:Demosaicing}.

>>>>

A bayer filter is a type of color filter array (CFA). The majority of digital image sensors in digital cameras and phones use a Bayer filter mosaic pattern to arrange RGB color filters on the sensor. The pattern consists of 50\% green, 25\% red, and 25\% blue pixels \cite{wiki:BayerFilter}. This ratio emulates the color sensitivity of the human eye. Due to this pattern on the sensor, the raw output of a digital camera also has each pixel filtered to only red, green, or blue and a demosaicing algorithm must be used to interpolate the other values for each pixel \cite{wiki:BayerFilter}.

@@

A demosaicing algorithm reconstructs a full color image from the separate red, green, or blue only pixels from an image sensor with a CFA \cite{wiki:Demosaicing}. There are many methods for this, the simplest ones interpolate the values for the other two color channels of a given pixel based on nearby pixels from the CFA image of those colors.
